---
title: "R Notebook"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

1.  Let $x_1, \ldots , x_n$ be a random sample (iid) from some
    distribution $F_\theta$ with the unknown parameter $\theta$. Which
    of the three one-sample tests ($t$-test, sign test or signed rank
    test) would you use (and why!) to test whether the location
    (expected value/median) of the data is equal to 1 if we know for
    certain that the distribution $F_\theta$ is

    1.  an exponential distribution with unknown rate parameter
        $\theta$,
        
        Sign test, as the ditribution is not symmetric nor normal
        
    2.  a normal distribution with variance 2 and unknown expected value
        $\theta$,
        
        t-test, as the distribution is normal
        
    3.  a Laplace distirbution with known scale parameter 5 and unknown
        location parameter $\theta$,
        
        signed rank test as the dist is symmetric but not normal
        
    4.  a Poisson distirbution with unknown parameter $\theta$?
    
        sign test, as the ditribution is not symmetric nor normal
    

2.  The data set airmiles lists the passenger miles flown by commercial
    airlines in the United States for each year from 1937 to 1960. To
    inspect whether the yearly passenger miles equal 10000 on average, a
    researcher performed a sign test to test the null hypothesis
    $med_x = 10000$ on significance level 5% with the results shown
    below and concluded that there is no evidence against the null
    hypothesis. Do you agree with the researcher's conclusion? 
    
    ```{r}
    airmiles
    ```
    
    ```{r}
    binom.test(sum(airmiles > 10000), length(airmiles))
    ```

P value is actually much greates than \alpha (0.05), so \H\_0 should not be rejected.